\documentclass{ucbthesis}
\usepackage{mathrsfs, graphicx, bm}
\usepackage{cite}
% \usepackage{floatrow}

\usepackage{amsmath,amssymb,amsfonts,hyperref,lineno,microtype,setspace,multicol,textcomp, marvosym, algorithm,algpseudocode, algorithmicx, wrapfig, mathtools}

% To-do notes
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}
\newcommand{\mytodo}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}


% Set graphics path
\graphicspath{ {figures/} }

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}

\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

\renewcommand{\vec}{\bm}
\newcommand{\op}{\mathcal}
\newcommand{\mat}{\mathbf}

\newcommand{\object}{\vec{x}}
\newcommand{\kernel}{\vec{h}}
\newcommand{\h}{\kernel}
\newcommand{\x}{\object}
\newcommand{\image}{\vec{y}}
\newcommand{\y}{\image}
\newcommand{\noise}{{\eta}}
\newcommand{\blurmat}{\mat{B}}
\newcommand{\B}{\blurmat}
\newcommand{\crop}{\mat{W}}
\newcommand{\W}{\crop}
\newcommand{\A}{\mat{A}}
\newcommand{\I}{\mat{I}}
\newcommand{\e}{\vec{e}}
\newcommand{\D}{\mat{D}}
\newcommand{\M}{\mat{M}}
\newcommand{\F}{\mat{F}}
\renewcommand{\top}{\mathsf{H}}


\begin{document}


\bibliographystyle{osajnl}

% Declarations for Front Matter
\title{Quantitative Microscopy using Coded Illumination}
\author{Zachary Fitzgerald Phillips}
\degreesemester{Spring}
\degreeyear{2019}
\degree{Doctor of Philosophy}
\chair{Associate Professor Laura Waller}
\othermembers{Professor Lydia Sohn \\ Assistant Professor Ren Ng}
\numberofmembers{3}

\field{Applied Science and Technology}
\campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
% \approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

% Dedication
\begin{dedication}
  \include{dedication}
\end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures

\clearpage
\begin{acknowledgements}
First and foremost, I would like to thank my advisor Laura Waller for providing careful guidance throughout my time at Berkeley, and for putting faith and resources behind myself and fellow lab members so that we can freely explore, create, and publish in the field of computational imaging. I would also like to thank my committee, Assistant Professor Ren Ng and Professor Lydia Sohn, for many useful conversations throughout my time at UC Berkeley. The Waller Lab has been a fantastic place to learn about the field of computational imaging, and I am grateful to each of my fellow group members. I would like to specifically thank my co-authors and collaborators within the Waller lab, including Regina Eckert, Gautam Gunjala, Michael Kellman, Nick Antipa, and David Ren. Specifically, I would like to thank Michael Chen for being an excellent collaborator in both research and entrepreneurship, and my closest neighbor, Li-Hao Yeh, with whom I have enjoyed thousands of conversations during our nearly 5 years in 558 Cory Hall. I have genuinely enjoyed my many whiteboard discussions with Sarah Dean, and feel very fortunate to have worked extensively with Post-docs Lei Tian, Volker Jaedicke, Shwetadwip Chowdhury, and Emrah Bostan. I would also like to acknowledge those who took the time to proofread this dissertation through its many iterations who have not already been mentioned: Kristina Monokhova, Michael Kellman, Henry Pinkard, and Emma Alexander.

During my time at Berkeley, I found that being productive and focused during the week requires taking time to unwind during the weekend (and occasionally during the evening). I would first like to thank my girlfriend, Chelsea, for always being a steadfast adventure partner and sounding board through the many seasons of graduate school. Since my first days in Berkeley, I've enjoyed many waves and adventures with my close friend and fellow AS\&T student Brandon Wood. I also want to thank my friends Chris Lalau-Keraly, Alex Forse, Kyle Ginthner, JB Chapman, (Day-leader) Mike Chapman, Jon Morris, Alix Charles, Mike Francis, Dan Wooten, and many others for our many good times.

Attending Berkeley has been my proudest and must fulfilling accomplishment, and it would have never been possible without my Mom, Dad, and sisters Allie and Mandie, who have always been supporting through our shared challenges as well as my own. I credit my dad, together with my grandfather, for teaching me how to break down a complicated problem into a series of small problems, and the importance of tenacity. My mother taught me the importance of a sense of humor and being personable. I would also like to acknowledge all of my grandparents, especially Phil and Bertha Phillips, who continue to teach importance of family, travel, and spending time outdoors.

I also want to thank those who helped and encouraged me prior to coming to Berkeley, including Professor Amy Oldenburg, Daniel Marks, and Raghav Chhetri.

Finally, I want to thank the many undergraduate students I've worked with, including Patrick Oare, Joel Whang, Nitin Sadras, Aditya Gande, Gautam Gunjala, Sachin Deyoung, Taehyung Kim, Paroma Varma, Jared Rulison, Sudarshan Seshadri, and Kuan Chang for their generous assistance despite their many obligations.

\end{acknowledgements}

\end{frontmatter}
\pagestyle{headings}
\include{chap1_introduction}
\include{chap2_phase}
\include{chap3_high_throughput}
\include{chap4_fabrication}
\include{chap5_self_calibration}
\include{chap6_conclusion}
\include{appendix}

\bibstyle{osajnl}
\bibliography{references}

\end{document}
